Constant-round Blind Classical Verification of Quantum Sampling

### 2021-09-30 blind.tex
Fix singular/plural "for all" issues

\begin{thm} \label{thm:compiler-errors}
    For all cheating $\BQP$ prover $\Pblindstar$, there exists a cheating $\BQP$ prover $\Pstar$ s.t. for all $\lambda$ and input $x\in\zo^{\poly(\lambda)}$, the output distributions of $(\Pblindstar, \Vblind(x))$ and $(\Pstar, V)(x)$ are identical.
\end{thm}
\begin{proof}
    We define $\Pstar$ as follows.

@@

Finally, we show the blindness of $\Piblind$ through a standard hybrid argument:
\begin{thm} \label{thm:compiler-blindness}
    Under the QLWE assumption with polynomial modulus, $\Piblind$ is blind.
\end{thm}
\begin{proof}
    We show that for all cheating $\BQP$ prover $P^*$, $\lambda\in\bbN$, $x\in\zo^n$,
    $P^*$ cannot distinguish $(P^*, \Vblind(x))(1^\lambda)$ from $(P^*, \Vblind(0^n))(1^\lambda)$ with noticeable probability in $\lambda$.
    We use a hybrid argument; let $\Hyb_{T+1}^x=(P^*, \Vblind(x))(1^\lambda)$ and $\Hyb_{T+1}^0=(P^*, \Vblind(0^n))(1^\lambda)$.
    For $2\leq t<T+1$, define $\Hyb_t^x$ to be the same as $\Hyb_{t+1}^x$,
    except when $\Vblind$ should send $\ctx{v}{t}{t}$ and $\ctx{sk}{t-1}{t}$, it instead sends encryptions of $0$ under $pk_t$.
    We define $\Hyb_1^x$ to be the same as $\Hyb_2^x$ except the verifier sends encryptions of $0$ under $pk_1$ in place of $\ctx{x}{}{1}$ and $\ctx{v}{1}{1}$.
    We define $\Hyb_t^0$ similarly. Note that $\Hyb_1^x$ and $\Hyb_1^0$ are identical.

>>>>

\begin{thm} \label{thm:compiler-errors}
    For all cheating $\BQP$ provers $\Pblindstar$, there exists a cheating $\BQP$ prover $\Pstar$ s.t. for all $\lambda$ and inputs $x\in\zo^{\poly(\lambda)}$, the output distributions of $(\Pblindstar, \Vblind(x))$ and $(\Pstar, V)(x)$ are identical.
\end{thm}
\begin{proof}
    We define $\Pstar$ as follows.

@@

Finally, we show the blindness of $\Piblind$ through a standard hybrid argument:
\begin{thm} \label{thm:compiler-blindness}
    Under the QLWE assumption with polynomial modulus, $\Piblind$ is blind.
\end{thm}
\begin{proof}
    We show that for all cheating $\BQP$ provers $P^*$, $\lambda\in\bbN$, $x\in\zo^n$,
    $P^*$ cannot distinguish $(P^*, \Vblind(x))(1^\lambda)$ from $(P^*, \Vblind(0^n))(1^\lambda)$ with noticeable probability in $\lambda$.
    We use a hybrid argument; let $\Hyb_{T+1}^x=(P^*, \Vblind(x))(1^\lambda)$ and $\Hyb_{T+1}^0=(P^*, \Vblind(0^n))(1^\lambda)$.
    For $2\leq t<T+1$, define $\Hyb_t^x$ to be the same as $\Hyb_{t+1}^x$,
    except when $\Vblind$ should send $\ctx{v}{t}{t}$ and $\ctx{sk}{t-1}{t}$, it instead sends encryptions of $0$ under $pk_t$.
    We define $\Hyb_1^x$ to be the same as $\Hyb_2^x$ except the verifier sends encryptions of $0$ under $pk_1$ in place of $\ctx{x}{}{1}$ and $\ctx{v}{1}{1}$.
    We define $\Hyb_t^0$ similarly. Note that $\Hyb_1^x$ and $\Hyb_1^0$ are identical.

### 2021-09-30 model.tex
Fix singular/plural "for all" issues

\begin{definition}
    \label{dfn:stats-secure-proto-sampbqp}
    Let $\Pi=(P, V)$ be a $\QPIP_\tau$ protocol.
    We say it is a protocol for the $\SampBQP$ instance $(D_x)_{x\in\zo^*}$ with completeness error $c(\cdot)$ and statistical (resp., computational) soundness if the following holds:
    \begin{itemize}
        \item On public inputs $1^\lambda$, $1^{1/\eps}$, and $x\in\zo^{\poly(\lambda)}$, $V$ outputs $(d, z)$ where $d\in\set{\Acc, \Rej}$.
            If $d=\Acc$ then $z\in\zo^{m(\abs{x})}$ where $m$ is given in \Cref{dfn:sampling-problem}, otherwise $z=\bot$.
        \item (Completeness):
            For all accuracy parameter $\eps(\lambda)=\frac{1}{\poly(\lambda)}$,
            security parameter $\lambda\in\bbN$,
            and $x\in\zo^{\poly(\lambda)}$,
            let $(d, z)\leftarrow(P, V)(1^\lambda, 1^{1/\eps}, x)$, then $d=\Rej$ with probability at most $c(\lambda)$.
        \item (Statistical soundness): For all cheating prover $P^*$,
            accuracy parameter $\eps(\lambda)=\frac{1}{\poly(\lambda)}$,
            sufficiently large $\lambda\in\bbN$, and $x\in\zo^{\poly(\lambda)}$,
            consider the following experiment:
            \begin{itemize}
                \item Let $(d, z)\leftarrow(P^*, V)(1^\lambda, 1^{1/\eps}, x)$.
                \item Define $z_{ideal}$ by
                $$\begin{cases}
                    z_{ideal}=\bot & \text{if } d=\Rej\\
                    z_{ideal}\leftarrow D_x & \text{if } d=\Acc
                \end{cases}$$.
            \end{itemize}
            It holds that $\norm{(d,z)-(d,z_{ideal})}_{\mathrm{TV}}\leq\eps$.
		\item (Computational soundness):
        For all cheating $\BQP$ prover $P^*$, $\BQP$ distinguisher $\mathsf{D}$, accuracy parameter $\eps(\lambda)=\frac{1}{\poly(\lambda)}$,
            sufficiently large $\lambda\in\bbN$, and all $x\in\zo^{\poly(\lambda)}$,
            let us define $d, z, z_{ideal}$ by the same experiment as above.
            It holds that $(d, z)$ is $\eps$-computationally indistinguishable to $(d, z_{ideal})$ over $\lambda$.
    \end{itemize}
\end{definition}

>>>>

\begin{definition}
    \label{dfn:stats-secure-proto-sampbqp}
    Let $\Pi=(P, V)$ be a $\QPIP_\tau$ protocol.
    We say it is a protocol for the $\SampBQP$ instance $(D_x)_{x\in\zo^*}$ with completeness error $c(\cdot)$ and statistical (resp., computational) soundness if the following holds:
    \begin{itemize}
        \item On public inputs $1^\lambda$, $1^{1/\eps}$, and $x\in\zo^{\poly(\lambda)}$, $V$ outputs $(d, z)$ where $d\in\set{\Acc, \Rej}$.
            If $d=\Acc$ then $z\in\zo^{m(\abs{x})}$ where $m$ is given in \Cref{dfn:sampling-problem}, otherwise $z=\bot$.
        \item (Completeness):
            For all accuracy parameters $\eps(\lambda)=\frac{1}{\poly(\lambda)}$,
            security parameters $\lambda\in\bbN$,
            and $x\in\zo^{\poly(\lambda)}$,
            let $(d, z)\leftarrow(P, V)(1^\lambda, 1^{1/\eps}, x)$, then $d=\Rej$ with probability at most $c(\lambda)$.
        \item (Statistical soundness): For all cheating provers $P^*$,
            accuracy parameters $\eps(\lambda)=\frac{1}{\poly(\lambda)}$,
            sufficiently large $\lambda\in\bbN$, and $x\in\zo^{\poly(\lambda)}$,
            consider the following experiment:
            \begin{itemize}
                \item Let $(d, z)\leftarrow(P^*, V)(1^\lambda, 1^{1/\eps}, x)$.
                \item Define $z_{ideal}$ by
                $$\begin{cases}
                    z_{ideal}=\bot & \text{if } d=\Rej\\
                    z_{ideal}\leftarrow D_x & \text{if } d=\Acc
                \end{cases}$$.
            \end{itemize}
            It holds that $\norm{(d,z)-(d,z_{ideal})}_{\mathrm{TV}}\leq\eps$.
		\item (Computational soundness):
        For all cheating $\BQP$ provers $P^*$, $\BQP$ distinguishers $\mathsf{D}$, accuracy parameters $\eps(\lambda)=\frac{1}{\poly(\lambda)}$,
            sufficiently large $\lambda\in\bbN$, and all $x\in\zo^{\poly(\lambda)}$,
            let us define $d, z, z_{ideal}$ by the same experiment as above.
            It holds that $(d, z)$ is $\eps$-computationally indistinguishable to $(d, z_{ideal})$ over $\lambda$.
    \end{itemize}
\end{definition}

### 2021-09-30 preliminaries.tex
Fix singular/plural "for all" issues

\begin{definition}
    Let $\Pi=(P, V)$ be a $\QPIP_\tau$ protocol.
    We say it is a protocol for a $\BQP$ language $L$ with completeness error $c(\cdot)$ and soundness error $s(\cdot)$ if the following holds:
\begin{itemize}
        \item On public input $1^\lambda$ and $x\in\zo^*$, the verifier outputs either $\Acc$ or $\Rej$.
        \item (Completeness): For all security parameter $\lambda\in\bbN$ and $x\in\zo^{\poly(\lambda)}$, if $x\in L$ then
        $\Pr\left[(P, V)(x, 1^\lambda)=\Rej\right]<c(\lambda)$.
        \item (Soundness): For all cheating $\BQP$ prover $P^*$, sufficiently large \\security parameter $\lambda\in\bbN$, and $x\in\zo^{\poly(\lambda)}$, if $x \notin L$ then \\$\Pr\left[(P, V)(x, 1^\lambda)=\Acc\right]<s(\lambda)$.
    \end{itemize}
\end{definition}

@@

\begin{definition}[Blindness]
    Let $\Pi=(P, V)$ be an interactive protocol with common inputs $1^\lambda$ 
    %(and $1^{1/\eps}$ for the case of $\SampBQP$ problem), 
    and verifier's private input $x\in\zo^*$.
    We say $\Pi$ is \emph{blind} if for all cheating $\BQP$ prover $P^*$ the following ensembles are computationally indistinguishable over $\lambda$:
    \begin{itemize}
        \item $\set{\View_{P^*}(P^*, V(x))(1^\lambda)}_{\lambda\in\bbN, \eps\in(0,1), x\in\zo^*}$,
        \item $\set{\View_{P^*}(P^*, V(0))(1^\lambda)}_{\lambda\in\bbN, \eps\in(0,1), x\in\zo^*}$.
    \end{itemize}
\end{definition}

>>>>

\begin{definition}
    Let $\Pi=(P, V)$ be a $\QPIP_\tau$ protocol.
    We say it is a protocol for a $\BQP$ language $L$ with completeness error $c(\cdot)$ and soundness error $s(\cdot)$ if the following holds:
\begin{itemize}
        \item On public input $1^\lambda$ and $x\in\zo^*$, the verifier outputs either $\Acc$ or $\Rej$.
        \item (Completeness): For all security parameters $\lambda\in\bbN$ and $x\in\zo^{\poly(\lambda)}$, if $x\in L$ then
        $\Pr\left[(P, V)(x, 1^\lambda)=\Rej\right]<c(\lambda)$.
        \item (Soundness): For all cheating $\BQP$ provers $P^*$, sufficiently large \\security parameters $\lambda\in\bbN$, and $x\in\zo^{\poly(\lambda)}$, if $x \notin L$ then \\$\Pr\left[(P, V)(x, 1^\lambda)=\Acc\right]<s(\lambda)$.
    \end{itemize}
\end{definition}

@@

\begin{definition}[Blindness]
    Let $\Pi=(P, V)$ be an interactive protocol with common inputs $1^\lambda$ 
    %(and $1^{1/\eps}$ for the case of $\SampBQP$ problem), 
    and verifier's private input $x\in\zo^*$.
    We say $\Pi$ is \emph{blind} if for all cheating $\BQP$ provers $P^*$ the following ensembles are computationally indistinguishable over $\lambda$:
    \begin{itemize}
        \item $\set{\View_{P^*}(P^*, V(x))(1^\lambda)}_{\lambda\in\bbN, \eps\in(0,1), x\in\zo^*}$,
        \item $\set{\View_{P^*}(P^*, V(0))(1^\lambda)}_{\lambda\in\bbN, \eps\in(0,1), x\in\zo^*}$.
    \end{itemize}
\end{definition}

### 2021-09-30 qpip0.tex
Fix singular/plural "for all" issues

	For all $i\in[m]$, $\gamma \in \L\{\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}\R\}$, there exist two $\poly(1/\gamma_0,T,\lambda)$-time quantum circuit with post selection\footnote{A quantum circuit with post selection is composed of unitary gates followed by a post selection on some measurement outcome on ancilla qubits, so it produces a subnormalized state, where the amplitude square of the output state is the probability of post selection.} $G_{0,i,\gamma}$ and $G_{1,i,\gamma}$ such that for all (possibly sub-normalized)  quantum state $\ket{\psi}_{\regX,\regZ}\in  H_{\regX,\regZ}$,  properties \ref{property:partition-err}~\ref{property:partition-testing}~\ref{property:partition-binding}~\ref{property-partition-norm-sum}, to be described later, are satisfied. Before we describe the properties, we introduce the following notations:

>>>>

	For all $i\in[m]$, $\gamma \in \L\{\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}\R\}$, there exist two $\poly(1/\gamma_0,T,\lambda)$-time quantum circuit with post selection\footnote{A quantum circuit with post selection is composed of unitary gates followed by a post selection on some measurement outcome on ancilla qubits, so it produces a subnormalized state, where the amplitude square of the output state is the probability of post selection.} $G_{0,i,\gamma}$ and $G_{1,i,\gamma}$ such that for all (possibly sub-normalized)  quantum states $\ket{\psi}_{\regX,\regZ}\in  H_{\regX,\regZ}$,  properties \ref{property:partition-err}~\ref{property:partition-testing}~\ref{property:partition-binding}~\ref{property-partition-norm-sum}, to be described later, are satisfied. Before we describe the properties, we introduce the following notations:
